This project is intended to be deployed to senior citizen homes as well as locations that desire a fully automated louvre control.
Plantation shutters are attractive attachments to any home or building and helps conserve heat as well as requires less intensive cleaning. Because of its benefits, many buildings take to having multiple plantation shutters located in various rooms in various sizes. In some installed spots, it is difficult to reach the shutters and as such are left inaccessible and unused.
 Even though they are great additions to certain homes and buildings, if they are not easy to access, the plantation shutters can be seen as an inconvenience. For easy deployment to retirement homes, it is necessary to simplify the use of these shutters as residents are most likely not in the best physical state to manually handle these shutters.
 The same consideration goes to businesses like hospitals that have large scale shutters located around the premises even within multiple rooms. Having to walk around the halls and operate these shutters probably multiple times a day would be very inefficient and tasking. Using a smartphone application to automatically open and close some or all the shutters in a complex even set controls based on a set schedule would be a massive step in convenience and bringing comfort without added stress
Then of course are the technological-driven individuals who aspire to have fully automated homes. Having a smart shutter that automatically opens and closes the louvres depending on sunrise and sunset as well as a quick option to operate all shutters in a room, a set of rooms or all the rooms with just a click of a button or an easily controlled slider bar would be a huge benefit to them as well as the added edge to their modernized complex.
Thus, the idea to automate plantation shutters came about to promote ease of use and comfort you don't have to work for.
