We have to work with two more difference teams for this project, one EE team and one more CSE team. This project required to create a circuit board with a chip that can receive a signal from an application to do action shut and open. We need electrical lap to create and testing the circuit board, that require soldering tool, electrical component for the board like resistor, capacitor, fuse, relay, transistor ... beside that we need and electric motor to create a force. A good design tool like Solidworks is needed for design circuit board. App team need computer with software to create android app and iOS app.\newline
Testing is needed all three teams to test separate first and collapse later for final test to make sure everything connect and working perfectly. We use electric testing kit like ohmmeter to check electric stuff and use unit testing to check our code.  For using the design and coding software we need to take time to look up and learn on google. There are some online class teaching how to code and design but we try to use both way to help us saving time to get our work done. All the electrical tools we use are available in the laps like pliers,magnetic screwdrivers.We do have 3D printer in the lap too but we have to pay for the material 1.75mm PLA Filament. There are some color for the filament with difference price and we chose the cheapest to save money. We also try to print our gear instead of order them form Amazon. \newline 
Some electrical components like chips, resistors, etc we need to order from Amazon or Ebay.\newline
Software are free to download and install and we just use our computer. We also use Github to share code, Slack and Groupme communicate with stakeholders and sponsors.We create two groups of Groupme, one for our team and one for sponsor communication. In that way we can keep track of our work and have more efficient way to communicate with team mate and sponsor.  




