
Automation of the surrounding environment of a modern human being allows increasing his work efficiency and comfort.\cite{Patz2013}. Our product is design to help handicap person who disability to walk or can not walk normally to open and shutdown the window by automation.Beside that, our Smart Shutter will be a helpful product for commercial building to control all the windows individual or grouping windows.Bluetooth has become the standard technology for external interfacing to laptop PCs and mobile devices\cite{Hansen} that is the reason why we chose Bluetooth connection for Smart Shutter. Home Automation System (HAS) using Android for Mobile Phone\cite{Panth2011} and we try to do the same thing by using Bluetooth connection for each individual windows. All windows are connected to wireless device and then connect to mobile device. So our product support and application in both android and iOS.Android is a technology platform with its own ecosystem of tools to support it\cite{Gerber}, and we decide to use Android Studio for our Android app.Basic understanding about iOS App Development\cite{Chang} is helping us with iPhone app. By just install our product, customer can open or shut down window all the way or half way depend on what the prefer. They can schedule open and shutdown windows on sunrise and sunset. With our product, customer can enjoyed a nice scene outside just by one second. Imagine about a patient who just have a surgery can open the window without helping form a nurse or another person. It helps the patient for not waiting for help, and also the nurse to save time and help other patient. If one leaf can giving hope like The Last leaf of O'Henry, our Smart Shutter will bring people more for our customer.



