The main stakeholder of our project is Frank Gronteman and CSE-4316 Professor Christopher D. McMurrough. Frank is an engineer and want to make the smart shutter project in a commercial level. The smart shutter will be developed to be used in commercial buildings like hospital, senior retirement homes and residential homes and business areas. \newline
Since the responsibility of the project has 3 separate teams which include EE team, embedded team and application team. EE team has the responsibility of developing the hardware and controller that controls the smart shutter. Embedded development team and our teams will work in microcontroller firmware, communication protocol and app interface. The project contains 3 teams; therefore, communication and exchange of information is a must. We would be communicating with teams and sponsors via an app called GroupMe. We have created the groups for all the teams and its members and sponsors to chat about the project. \newline
Since everyone is busy, we have decided to use GroupMe app and share their work through the app. Everyone will contribute in accomplishing the project. We can contact Frank via cellphone, email and GroupMe app. He has shared us his contact information in our recent meeting. Frank will hold the meetings in which we can discuss about our progress in the project. \newline
For our team, we will be chatting through GroupMe. We are going to meet with each other after the class for 15 minutes as sprint meeting and discuss about the project and assign the topic to be solved. We will have to divide the work and accomplish the task. If anyone cannot figure out the topic then we will bring that topic to everyone attention and try to solve it through meetings and discussion. If we need to have extra meeting, then we will fix the date and time through sprint meeting. \newline
Scrum Master : Umesh Shrestha 
Project Owner : Khoa Huynh
Our team will change the role of scrum master in every sprint cycle.  
